\title{Matthew Olson Resume}
\documentclass[11pt, a4paper]{resume}

\begin{document}
	\begin{center}
    	{\fontsize{26pt}{1em}\headerfontlight\color{gray} Matthew E. Olson}
        \vspace{1mm}
    	\\
    	{\fontsize{6.8pt}{1em}\headerfont\color{darkgray}
    		{\faHome\ 4571 Foxtail Cir, Greenwood Village, CO} \, | \,
    		{\faMobile\ (303) 514-7424} \, | \,
    		{\faEnvelope\ molson194@gmail.com} \, | \,
    		{\faUser\ molson194.tk} \, | \,
    		{\faGithubSquare\ molson194} \, | \,
    		{\faLinkedinSquare\ molson194}
    	}
    \end{center}
    \par\addvspace{1.5ex}
    
    \fancyfoot[L]{\footerstyle{\today}}
  	\fancyfoot[C]{\footerstyle{Matthew E. Olson~~~·~~~Résumé}}
  	\fancyfoot[R]{\footerstyle{\thepage}} 

\cvsection{Education}
\begin{cventries}
  \cventry
    {Electrical and Computer Engineering (B.S.E.), Physics (B.A.), and Computer Science (Minor)}
    {Duke University}
    {Durham, NC}
    {2013-2017}
    {
      \begin{cvitems}
        \item {Cumulative GPA: 3.8}
        \item {Relevant Coursework: Data Structures and Algorithms in Java, Computer Architecture, Quantum Physics, Circuits}
        \item{Academic Chair of Pi Kappa Phi Fraternity. Member of Club Soccer Team. HackDuke participant}
      \end{cvitems}
    }
  \cventry
  	{Cum Laude Scholar, Class of 2013 Math and Science Award}
    {Kent Denver School}
    {Englewood, CO}
    {2009-2013}
    {
    	\begin{cvitems}
        	\item {Cumulative GPA: 4.3}
            \item {Editor-in-Chief of newspaper. Authored 18 articles. Managed 40 members. CHSPC Award.}
            \item {Soccer Captain. State Finalist. Deso Leadership Award. All-Conference. 33 career varsity goals.}
        \end{cvitems}
    }
\end{cventries}

\cvsection{Experience}
\begin{cventries}
  \cventry
    {Software Engineering Intern}
    {Chesapeake Technology International}
    {Denver, CO}
    {Summer 2015 - Summer 2016}
    {
      \begin{cvitems}
        \item {Worked on RaptorX, a real-time visualization and control software for military operations}
        \item {Derived algorithm for cell tower usage, applied to data in RaptorX, and created elements to visualize electromagnetic spectrum}
        \item {Fixed bugs and improved code to improve military control of assets during operations}
      \end{cvitems}
    }
  \cventry
    {Engineering Intern in Failure Analysis Department}
    {Echostar Corporation}
    {Englewood, CO}
    {Summer 2014}
    {
      \begin{cvitems}
        \item {Tested and improved the functionality of automated testing devices for digital video recorders}
        \item {Found and replaced faulty components on digital video recorders using circuit schematic and multimeter}
      \end{cvitems}
    }
  \cventry
    {Software Engineering Intern}
    {Secure64 Software Corporation}
    {Greenwood Village, CO}
    {Summer 2013}
    {
      \begin{cvitems}
        \item {Worked on Gr8Privacy, a file sharing encryption software. Presented demos and helped raise \$1.15 million in funding}
        \item {Designed and set up web page using WordPress. Found bugs and improvements in Gr8Privacy software}
      \end{cvitems} 
    }
  \cventry
  	{Memristor and Tunnel Diode Research}
    {Independent Physics Laboratory}
    {Durham, NC}
    {2015 - Present}
    {
      \begin{cvitems}
        \item {Derived switching characteristics of stochastic nonlinear electronic transport and designed switching circuit with tunnel diode}
        \item {Tested noise induced switching on memory devices, homemade memristors, and neuronal transport}
      \end{cvitems}
    }
  \cventry
    {Teacher's Assistant}
    {Duke University Engineering Department}
    {Durham, NC}
    {2014-2016}
    {
      \begin{cvitems}
        \item {Led lab, recitation, held office hours, and graded assignments for Computer Science 250 and Engineering 103}
      \end{cvitems}
    }
\end{cventries}

\cvsection{Technical Skills}
	\par\addvspace{0.5ex}
	\setlength\tabcolsep{0pt}
  	\setlength{\extrarowheight}{0pt}
  	\begin{tabular*}{\textwidth}
    {@{\extracolsep{\fill}} L{18cm} R{0cm}}
    \descriptionstyle{
		\begin{cvitems}
        \item {Java, C, Python, Swift, Objective-C, C++, MIPS Assembly, Matlab, Labview, HTML, CSS, Git, Linux, WordPress}
        \item {Graphic Design. Proficient with Illustrator, InDesign, and Photoshop. Made all designs for projects}
      \end{cvitems}  
    }
    \end{tabular*}
        
\cvsection{Side Projects}
	\par\addvspace{0.5ex}
	\setlength\tabcolsep{0pt}
  	\setlength{\extrarowheight}{0pt}
  	\begin{tabular*}{\textwidth}
    {@{\extracolsep{\fill}} L{18cm} R{0cm}}
    \descriptionstyle{
		\begin{cvitems}
        \item {Created Dare Devil: A social media platform for dares. Facebook integration for friends and Stripe integration for crowdfunding.}
        \item{Relased Spider! to the Mac App Store: Simple spider solitaire game for the Mac. Built in 5 days.}
        \item{Southwest Checkin: Python script used to check into southwest flight and get the best boarding position}
        \item{Duke Enroll: Automated python script used to enroll a student in classes, so the student gets classes before they fill up}
        \item{Pipelined Processor: Built in Verilog HDL for FPGA with multiplier/divider, ALU, and register file}
      \end{cvitems}  
    }
    \end{tabular*}
    
\cvsection{Personal}
	\par\addvspace{0.5ex}
	\setlength\tabcolsep{0pt}
  	\setlength{\extrarowheight}{0pt}
  	\begin{tabular*}{\textwidth}
    {@{\extracolsep{\fill}} L{18cm} R{0cm}}
    \descriptionstyle{
		\begin{cvitems}
        \item{Hobbies include philosophy, investing, travel, rock climbing, fantasy football, soccer, basketball, tennis, and Ping-Pong}
        \item {Duke Basketball fan (tented for 4 weeks), Rubik's cube solver (90 seconds), Juggler (almost 4 balls), Half-Marathon Finisher (1:31)}
      \end{cvitems}  
    }
    \end{tabular*}
    
    
\end{document}
